---
title: " Novel CoronaVirus in India: A Brief Analysis"
author: "Akshay Hareshbhai Sitlani"
date: "03/05/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(warn = -1)
```
**Welcome!**
<br>
<br> My name is **Akshay Hareshbhai Sitlani** and I am a student of MSDS - Statistics. I have done this project as a part of the subject **Data Wrangling and Husbandry** taught by Professor **Jason M. Klusowski**.
<br>
<br> My project topic is based on the current global pandemic i.e. **Novel CoronaVirus**, also known as, **COVID-19**.
<br>
<br> In this project, I have conducted the following analyses:
<br> &emsp;&emsp; (1) Number of Samples and Individuals between March 13 and April 28.
<br> &emsp;&emsp; (2) Number of Positive Test Results between March 13 and April 28.
<br> &emsp;&emsp; (3) Trend of increase/decrease in percentage positive results between March 13 and April 28.
<br> &emsp;&emsp; (4) Comparison of negative and positive cases each day between March 13 and April 28.
<br> &emsp;&emsp; (5) Types and Count of Testing Centers in India.
<br> &emsp;&emsp; (6) Count of Testing Centers in various states in India.
<br> &emsp;&emsp; (7) State wise distribution of various Testing Centers in India.
<br> &emsp;&emsp; (8) Type and Count of Health-Care Facilities across various states of India.
<br> &emsp;&emsp; (9) Types and Count of Beds available in various states of India.
<br> &emsp;&emsp; (10) Daily Cases Trend for Top 9 States in India.
<br> &emsp;&emsp; (11) Number of Beds per Active Cases in India.
<br> &emsp;&emsp; (12) Animation of Rise in Confirmed Cases across Top 10 states between January 30 and April 28.
<br> &emsp;&emsp; (13) Novel CoronaVirus - India Dashboard.

<br>
<br> Let's begin by importing all the necessary libraries.
<br>
```{r libraries_import, include=FALSE}

# Here, I import the libraries that will be useful to me in this project. Now, some of these may not be used in the project. I was trying various things out!

library(ggplot2)
library(plotly)
library(grid)
library(gridExtra)
library(pscl)
library(leaflet)
library(scales)
library(RColorBrewer)
library(ggmap)
library(maptools)
library(rgeos)
library(sf)
library(Cairo)
library(rgdal)
library(dplyr)
library(waffle)
library(reshape2)
library(treemapify)
library(Hmisc)
library(tidyverse)
library(viridis)
library(ggthemes)
library(gganimate)
library(lubridate)
library(knitr)
library(DT)
library(highcharter)
library(magrittr)

```

<br> In the next segment, I import all the datasets I plan to work on to RStudio.
<br>

```{r all_datasets_import}

# Importing the COVID-19 Testing Details dataset

covid19_india_tests <- read.csv("/Coronavirus/ICMRTestingDetails.csv")

# Importing the COVID-19 Testing Details dataset

covid19_india_testlabs <- read.csv("/Coronavirus/ICMRTestingLabs.csv")

# Importing the Hospitals and Beds dataset

Hospitals_Data <- read.csv("/Coronavirus/HospitalBedsIndia.csv")

# Importing the COVID-19 State/Union Territory wise cases dataset

corona_data <- read.csv("/Coronavirus/covid_19_india.csv")

# Find the summary statistics of all the datasets here:

# summary(covid19_india_tests)
# summary(covid19_india_testlabs)
# summary(Hospitals_Data)
# summary(corona_data)


```

<br> For any dataset that I analyse here, 
<br>I start with basic data manipulation and cleaning, followed by analysis and visualization.
<br>
<br> Let's take a look at the medical testings conducted by **ICMR (Indian Council of Medical Research)** for COVID-19.
<br>

```{r ICMRTestingDetails_Cleaning}

# Dropping the "Source" column as it would be of no use to us in the analysis.

drops <- c("Source")
covid19_india_tests <- covid19_india_tests[ , !(names(covid19_india_tests) %in% drops)]

# Changing column names for better readability.

colnames(covid19_india_tests) <- c("SNo","Test_Date", "Total_Samples_Tested", "Total_Individuals_Tested", "Total_Positive_Cases")

# Extracting just the date part from the Test_Date column and converting it to a date type using as.Date()

covid19_india_tests$Test_Date <- substr(covid19_india_tests$Test_Date,1,8)
covid19_india_tests$Test_Date <- as.Date(covid19_india_tests$Test_Date, format = "%d/%m/%y")

# Removing those rows for which no data is available. That would be sr. no. 10,12 and 13
# We also need to remove those rows which dont provide information regarding the number of positive test results. They won't be useful to us. That would be sr. no. 14 and 15.

covid19_india_tests <- covid19_india_tests[-c(10,12,13,14,15),]

# Now for some rows, we don't have the value of total individuals tested. We will assume that total individuals tested is same as total samples tested. That would be for sr. no 11, and 16 through 24.

count <- c(10:18,34:37)
for(i in count){
  covid19_india_tests$Total_Individuals_Tested[i] <- covid19_india_tests$Total_Samples_Tested[i]
}

covid19_india_tests <- covid19_india_tests[-c(30),] 

# Clearly, the number of samples tested is more than the number of individuals tested for many dates. That implies that some individuals have been tested more than once. That could mean that there is a higher probability to detect COVID_19 in such individuals on that particular day (Due to presences of false negatives). 

covid19_india_tests$Samples_Per_Individual <- covid19_india_tests$Total_Samples_Tested / covid19_india_tests$Total_Individuals_Tested
covid19_india_tests$Percent_Positive_Cases <- (covid19_india_tests$Total_Positive_Cases / covid19_india_tests$Total_Individuals_Tested) * 100

# We don't need the sr. no. column anymore. So we drop it.

drops <- c("SNo")
covid19_india_tests <- covid19_india_tests[ , !(names(covid19_india_tests) %in% drops)]

# Converting from a list type to a dataframe

covid19_india_tests <- data.frame(covid19_india_tests)

# Using melt() to merge data from two columns into one and creating such new dataframe

temp <- covid19_india_tests[,c("Test_Date","Total_Samples_Tested","Total_Individuals_Tested")]
colnames(temp) <- c("Test_Date","Samples","Individuals")

melted_data <- melt(temp,id.vars = "Test_Date")


# This is what my final data looks like:

head(melted_data,10)
tail(melted_data,10)
```

<br> So, my **ICMR Testing** data is ready for visualization.
<br>

```{r ICMRTestingDetails_visualizations, fig.height=10, fig.width=10}

# Visualizing totals samples and individuals tested over the given timeline using line chart plotted by melt().

ggplot(melted_data, aes(x=Test_Date, y=value, col=variable)) + 
  geom_line(size =2) +
  labs(title = "Samples Tested",
           x = "Dates", y = "Number of Tests")+
  theme( axis.line = element_line(colour = "darkblue", 
                      size = 1, linetype = "solid"),plot.title = element_text(hjust = 0.5))

# Visualizing the rise/drop of total positive cases over the timeline.

p1 <- ggplot(data=covid19_india_tests, aes(x=Test_Date, y=Total_Positive_Cases)) +
  geom_bar(stat="identity", fill= "red") +
  geom_smooth(method = "loess", color = "blue", formula = y~x)+
  labs(title = "Positive Test Results",
           caption = "*Empty spaces due to lack of data",
           x = "Dates", y = "Number of Positive Tests")+
  theme( axis.line = element_line(colour = "darkblue", 
                      size = 1, linetype = "solid"),plot.title = element_text(hjust = 0.5))

# Visualizing trend of percentage of positive cases over the timeline

p2 <- ggplot(data=covid19_india_tests, aes(x=Test_Date, y=Percent_Positive_Cases)) +
  geom_point() +
  geom_smooth(method = "loess",formula = y~x)+
  labs(title = "Percentage of Positive Test Results",
      caption = "*Empty spaces due to lack of data",
       x = "Dates", y = "Percentage of Positive Tests") +
  theme( axis.line = element_line(colour = "darkblue", 
                      size = 1, linetype = "solid"),plot.title = element_text(hjust = 0.5))

# Arranging p3 and p4 in a grid for better visuals.

grid.arrange(p1,p2)

# Visualizing total negative cases and total positive cases using a stacked bar graph. I use the plot_ly() from the library "plotly".

plot_ly(data=covid19_india_tests, x = ~Test_Date, y = ~(Total_Individuals_Tested-Total_Positive_Cases), type = 'bar', 
        name = 'Total Negative Cases',marker = list(color = 'darkblue')) %>%
        add_trace(y = ~Total_Positive_Cases, name = 'Total Positive Cases',marker = list(color = 'red')) %>%
        layout(yaxis = list(title = 'Count',gridwidth=2),xaxis=list(title = "Dates",gridwidth=2), barmode = 'stack', 
               title="Comparison of Negative Cases and Positive Cases", plot_bgcolor = "snow",
               annotations = list(x = 1, y = -0.1, text = "*Empty spaces due to lack of data", showarrow = F, xref='paper', 
                                  yref='paper', xanchor='right', yanchor='auto', xshift=0, yshift=0,font=list(size=12,          
                                                                                                              color="black")))  

```
<br> Let's draw insights from the generated graphs.
<br>
<br>**Insights:**
<br>
<br>**Graph:1**
<br>
<br>1. The increasing number of tests conducted in the latter half of the month period shows the proactiveness of the Government of India in arranging required medical facilities in short notice.
<br>
<br> 2. Both graphs are almost identical, with minor change in axis values.It can be noted in that period post 8th April, the gap between samples and individuals tested has increased, showing higher chances of an individual getting tested positive in first trial.
<br>
<br>**Graph:2**
<br>
<br> 1. More or less, we get a similar trend as the previous graph. So, the number of positive cases has been increasing almost exponentially.
<br>
<br> 2. In general, the percentage of positive cases has also increased over time.
<br>
<br>**Graph:3**
<br>
<br> 1. We can observe a positive correlation between total individuals tested and total positive cases.

<br> Now, let's move on to our next dataset which gives information regarding the availability of different types of testing labs in various parts of India.
<br>
```{r ICMRTestingLabs_Cleaning}

# Removing the columns not needed for analysis

keep <- c("state","type")
covid19_india_testlabs <- covid19_india_testlabs[keep]

# Changing column names for better readability

colnames(covid19_india_testlabs) <- c("State", "Facility_Type")

# Changing facility type into a factor variable. It will be useful while making visualizations.

covid19_india_testlabs$Facility_Type <- as.factor(covid19_india_testlabs$Facility_Type)

# Creating a dataframe to visualize the types of facilities.

types_of_facilities <- data.frame(table(covid19_india_testlabs$Facility_Type))
colnames(types_of_facilities) <- c("Type_Of_Facility","Count")

# Cleaning the data by editing names of some states to match them with those in the shapefile of India that we have.

levels(covid19_india_testlabs$State)[1] <- "Andaman and Nicobar"
levels(covid19_india_testlabs$State)[8] <- "Dadra and Nagar Haveli"

# Creating a new data frame which has information about number of labs in each state

labs_by_state <- table(covid19_india_testlabs$State)
labs_by_state <- data.frame(labs_by_state)
colnames(labs_by_state) <- c("State","Number_Of_Labs")

# Adding a few more states in our data frame which are present in the shapefile of indian map. For convenience, assigning zero as the number of labs in these states. Also, making some state name changes to help the visualization. Furthermore, one region i.e. Ladakh is given in our dataset, but it's not a state. It's part of Jammu and Kashmir. So, I have increased number of labs in Jammu and Kashmir and remove the row of "Ladakh" alltogether.

labs_by_state$State <- as.character(labs_by_state$State)
labs_by_state <- rbind(labs_by_state, c("Daman and Diu",0))
labs_by_state <- rbind(labs_by_state, c("Lakshadweep",0))
labs_by_state <- rbind(labs_by_state, c("Nagaland",0))
labs_by_state$State[33] <- "Uttaranchal"
labs_by_state$State[24] <- "Orissa"
labs_by_state$Number_Of_Labs[14] <- 5
labs_by_state <- labs_by_state[-c(18),]

# Arranging data by state names and making state variable a factor variable.

labs_by_state <- labs_by_state %>%
  arrange(labs_by_state$State)
labs_by_state$State <-as.factor(labs_by_state$State)
labs_by_state$Number_Of_Labs <-as.numeric(labs_by_state$Number_Of_Labs)

labs_by_state <- labs_by_state %>%
  arrange(Number_Of_Labs)
labs_by_state$State <- as.character(labs_by_state$State)
labs_by_state$State[4] <- "A and N"
labs_by_state$State[6] <- "D and NH"
labs_by_state$State[5] <- "Arunachal"

# Creating data depicting State/UT wise labs distribution

covid19_india_testlabs_1 <- covid19_india_testlabs%>%group_by(State,Facility_Type)%>%tally()

# Final data after necessary cleaning.

head(labs_by_state)
tail(labs_by_state)

```
<br> My **Testing Labs** data is now ready for visualization.

```{r ICMRTestingLabs_Visualizations, fig.height=10, fig.width=10}

# Visualization of types of Medical Testing Facilities using a waffle chart. 

waffle_data <- table(covid19_india_testlabs$Facility_Type)
waffle(waffle_data/3, rows=7, size=2, 
       colors=c("#EE82EE", "#9370DB", "#4B0082"), 
       title="Types of ICMR Testing Centres", 
       xlab="1 square: 3 centres",flip = F)+
  theme(plot.title = element_text(hjust = 0.5))

# Making a treemap to visualize the distribution of labs accross various states/union territories in India.

ggplot(labs_by_state, aes(area = Number_Of_Labs, fill = Number_Of_Labs,label = paste(State,Number_Of_Labs,sep="\n")))+
  geom_treemap() +
  geom_treemap_text(colour = "black", place = "centre",size = 15)+
  scale_fill_distiller(palette = "Paired")+
  labs(title = "Number of Testing Labs across States of India",fill = "Number of Labs")+
  theme(plot.title = element_text(hjust = 0.5))

# State/UT wise labs Distribution with their types. This provides a useful amalgamation of our treemap and waffle visualization.

ggplot(covid19_india_testlabs_1, aes(x=State, y=n))+
  geom_col(fill="hotpink")+
  theme_bw()+
  theme(axis.text.x=element_text(size=10, angle=90, hjust = 1, vjust = 0.5),plot.title = element_text(hjust=0.5))+
  xlab("States/UTs")+
  ylab("Count")+
  labs(title="State/UT-wise Labs Distribution")+
  facet_grid(~Facility_Type) +
  coord_flip()

```
<br>
**Important Facts about the above treemap:**
<br>
<br> 1. 3 states with no labs yet have been ommitted from the plot.These states are: Daman and Diu, Lakshadweep and Nagaland.
<br>
<br> 2. Some abbriviations have been used in the plot due to long state names and limited space on the plot. These abbreviations are: 
<br> A and N (Andaman and Nicobar), Arunachal (Arunachal Pradesh) and D and NH (Dadra and Nagar Haveli).
<br>
<br> **Insights:**
<br>
<br> 1. There are many government labs that are testing people for COVID-19. However, the private sector has not been given that discretion by the government. For fast detection and containment of this virus, private sector must be given equal if not more responsibility.
<br>
<br> 2. The states with the lighter color indicate that they have higher number of labs compared to the darket colored states. This could indicate two things: 
<br>
<br>&emsp;&emsp;(i). The positive part of this is that these states are forerunners is detecting and curing COIVD-19 affected people. States which are on the darker side, need special attention from the government. If more testing labs are not made available to them, it might lead to a bigger problem.
<br>
<br>&emsp;&emsp;(ii). The negative part of this is that the ligher colored states probably can have higher number of COVID-19 cases, due to which the government has set up more testing labs there in the first place. So, these states act like a hotspot and extra care need to be taken in such states so as to prevent further transmission esp. mass transmission.
<br>
<br> Let's move on to the next dataset. Here we explore the various medical care facilities and beds for patients available in India.
<br>
```{r HospitalBedsIndia_Cleaning}

# Removing the serial number column as it is of no use.

Hospitals_Data <- Hospitals_Data[,-c(1)]

# Changing column names for better readability

colnames(Hospitals_Data) <- c("States","Primary_Health_Centers","Community_Health_Centers","Sub_District_Hospitals","District_Hospitals","Public_Health_Facilities","Public_Beds","Rural_Hospitals","Rural_Beds","Urban_Hospitals","Urban_Beds")

# Cleaning and preprocessing data

Hospitals_Data[is.na(Hospitals_Data)] <- 0
Hospitals_Data[,2] <- as.numeric(levels(Hospitals_Data[,2]))[Hospitals_Data[,2]]
Hospitals_Data[37,2] <- 29899
Hospitals_Data <- Hospitals_Data[-c(37),]

# Here's what my final hospital beds data looks like:

head(Hospitals_Data,10)
tail(Hospitals_Data,10)
```
<br>
<br> My **Hospitals and Beds** data is now ready for visualization.
<br>
```{r HospitalBedsIndia_Visualizations, fig.height=10, fig.width=10}

# Setting margin parameters.

m <- list(l = 50, r = 50, b = 100, t = 100, pad = 4)

# Visualizing varial health care centers across different states.

plot_ly(Hospitals_Data, x = ~Hospitals_Data$States, y = ~Hospitals_Data$Primary_Health_Centers, type = 'bar', name = 'Primary Health Centers', marker = list(color = 'blue') , width = 1000, height = 1000)%>%
  add_trace(Hospitals_Data,y = ~Hospitals_Data$Public_Health_Facilities, name = 'Public Health Facilities', marker = list(color = 'purple')) %>%  
  add_trace(Hospitals_Data,y = ~Hospitals_Data$Rural_Hospitals, name = 'Rural Hospitals', marker = list(color = 'orange')) %>%  
  add_trace(Hospitals_Data,y = ~Hospitals_Data$Community_Health_Centers, name = 'Community Health Centers', marker = list(color = 'red'))%>% 
  add_trace(Hospitals_Data,y = ~Hospitals_Data$District_Hospitals, name = 'District Hospitals', marker = list(color = 'green')) %>%
  add_trace(Hospitals_Data,y = ~Hospitals_Data$Sub_District_Hospitals, name = 'Sub-District Hospitals', marker = list(color = 'hotpink')) %>%
  add_trace(Hospitals_Data,y = ~Hospitals_Data$Urban_Hospitals, name = 'Rural Beds', marker = list(color = 'cyan')) %>%
    layout(title = "Health Centers in India", xaxis = list(title = "States", tickangle = 90), yaxis = list(title = "Count"), margin = m, barmode = 'stack')

# Visualizing availability of public, urban and rural beds across different states.

plot_ly(Hospitals_Data, x = ~Hospitals_Data$States, y = ~Hospitals_Data$Public_Beds, type = 'bar', name = 'Public Beds', marker = list(color = 'blue'), width = 1000, height = 1000) %>%
    add_trace(Hospitals_Data[1:36,],y = ~Hospitals_Data$Urban_Beds, name = 'Urban Beds', marker = list(color = 'red'))%>% 
    add_trace(Hospitals_Data[1:36,],y = ~Hospitals_Data$Rural_Beds, name = 'Rural Beds', marker = list(color = 'green')) %>%
    layout(title = "Availability of Beds in India", xaxis = list(title = "States", tickangle = 90), yaxis = list(title = "Count"), margin = m, barmode = 'group')

```
<br>**Insights:**
<br> There are some states and/or Union Territories like Andaman and Nicobar Islands, Bihar, etc. that critically lack in hospitals, beds and other healthcare facilities. More focus should be given on increasing resources in such regions in order to contain the spread of COVID-19.
<br>
<br> Moving on to our final dataset, and probably the most important one. 
<br> The **Covid19 India** dataset contains all the information about active, recovered and deceased cases among other things. 
<br> Let's begin cleaning this data.
<br>
```{r covid_19_india_Cleaning}

# Removing the serial number column as it is of no use.

corona_data <- corona_data[,-c(1)]

colnames(corona_data) <- c("Date","Time","States","Confirmed_Indian","Confirmed_Foreigner","Cured","Deaths","Confirmed")

# Making a data frame showing the total confirmed cases grouped by states/union territories

confirmed_corona_data <- corona_data %>% 
group_by(`States`) %>% 
summarise(Total_Confirmed=max(Confirmed))

# Manipulating data to create animation of top 10 states with highest number of confirmed cases shown over a timeline.

# Adding a date column which will be used to animate over the timeline

my_date <- as.Date(corona_data$Date,"%d/%m/%y")
temp1 <- data.frame(date = c(my_date))
temp1 <- temp1 %>% 
  mutate(date = ymd(date)) %>% 
  mutate_at(vars(date), funs(year, month, day))

# Arrange data by state and date

new_corona_data<-cbind(corona_data,date=temp1[,1])
new_corona_data <-new_corona_data%>%
  group_by(States,date)

# Creating new dataframe for animation with selected columns from previously manipulated new_corona_data 

animation_corona_data <-data.frame(new_corona_data[3],new_corona_data[9],new_corona_data[8])

colnames(animation_corona_data)<-c("Detected_State","date","Cumulative_Sum")

# Create Index dataframe which ranks the states based on confirmed cases.

Index <- animation_corona_data %>%
  group_by(date) %>%
  mutate(rank = rank(-Cumulative_Sum,ties.method = "first")) %>%
  group_by(Detected_State) %>% 
  filter(rank <=10) %>%
  ungroup()

# Setting timeline greater than 30th January 2020.

Index<-Index[Index$date>="2020-01-30",]

# Creating daily trend dataframe with top 9 states. Performing inner join between new dataframe and original data having common id as "State.UnionTerritory".

corona_data$Date <-as.Date(corona_data$Date, format = "%d/%m/%y")
daily_case_trend_top9<-corona_data %>%
  filter(Date==max(Date))%>%
  top_n(9,Confirmed)
daily_case_trend_top9<-inner_join(corona_data,daily_case_trend_top9,"States")
daily_case_trend_top9<-daily_case_trend_top9%>%
  arrange(Date.x)%>%
  group_by(States)%>%
  mutate(per_day_cases = c(0,diff(Confirmed.x)))

# Preparing dataframe to find out number of beds per active cases.

beds_per_patient<-filter(corona_data,Date==max(Date))
beds_per_patient[,"Active"]<-beds_per_patient$Confirmed-(beds_per_patient$Deaths+beds_per_patient$Cured)
beds_per_patient<-filter(beds_per_patient,Active>0)
beds_per_patient<-inner_join(beds_per_patient,Hospitals_Data,by="States")
beds_per_patient[,"beds_to_act_case_ratio"]<-round(((beds_per_patient$Public_Beds+beds_per_patient$Rural_Beds + beds_per_patient$Urban_Beds)/beds_per_patient$Active),2)

```
<br>
<br> My **Covid19 India** data is now ready for visualization.
<br>
```{r covid_19_india_Visualizations}
# , fig.height=10, fig.width=10
# Visualizing the trend in the rise in daily cases.

ggplot(daily_case_trend_top9,aes(x=Date.x,y=Confirmed.x))+
  geom_point(color="violetred4")+
  geom_smooth(method="loess", formula = 'y~x')+
  theme_bw()+
  xlab("Period")+
  ylab("Cases Per Day")+
  labs(title="Daily case trend for top 9 states in India")+
  facet_wrap(~States)+
  theme(plot.title = element_text(hjust=0.5))

# Visualizing the number of beds per active patient.

ggplot(beds_per_patient, aes(x=States, y=beds_to_act_case_ratio,fill=States))+
  geom_bar(stat="identity")+
  labs(title = "Beds per Active Cases",
           x = "States/UTs", y = "Beds to Active Cases Ratio")+
  theme( axis.line = element_line(colour = "darkblue", 
                      size = 1, linetype = "solid"),
   axis.text.x = element_text(angle=90, vjust=0.6),plot.title = element_text(hjust=0.5),legend.position = "none")+
  ylim(0,6000)+
   geom_text(aes(label=beds_to_act_case_ratio,angle = 90), position=position_dodge(width=0.9), vjust=0.5,hjust = 0)

# Create Final Animation of Top 10 states with highest confirmed cases.

anim_plot <-  ggplot(Index, aes(rank, group = `Detected_State`, fill = as.factor(`Detected_State`), color = as.factor(`Detected_State`))) +
  geom_tile(aes(y = Cumulative_Sum/2, height = Cumulative_Sum, width = 0.9), alpha = 0.8, color = NA) +
  geom_text(aes(y = 0, label = paste(`Detected_State`, " ")), vjust = 0.2, hjust = 1) +
  coord_flip(clip = "off", expand = FALSE) +
  scale_y_continuous(labels = scales::comma) +
  scale_x_reverse() +
  guides(color = FALSE, fill = FALSE) +
  theme(axis.line=element_blank(), axis.text.x=element_blank(), axis.text.y=element_blank(), axis.ticks=element_blank(), axis.title.x=element_blank(),
        axis.title.y=element_blank(), legend.position="none", panel.background=element_blank(), panel.border=element_blank(), panel.grid.major=element_blank(),
        panel.grid.minor=element_blank(), panel.grid.major.x = element_line( size=.1, color="grey" ), panel.grid.minor.x = element_line( size=.1, color="grey" ),
        plot.title=element_text(size=25, hjust=0.5, face="bold", colour="grey", vjust=-1), plot.subtitle=element_text(size=18, hjust=0.5, face="italic", color="grey"),
        plot.caption =element_text(size=8, hjust=0.5, face="italic", color="grey"), plot.background=element_blank(),plot.margin = margin(2,2, 2, 4, "cm"))


final_anim <- anim_plot + transition_states(date, transition_length = 4, state_length = 1) +
  ease_aes('cubic-in-out')+
  view_follow(fixed_x = TRUE)  +
  labs(title = 'Date : {closest_state}', subtitle  =  "Top 10 States ", caption  = "Timeline of Confirmed Cases - Top 10 States")

# Execute the animation

animate(final_anim, 400, fps = 8,  width = 1200, height = 800,duration = 60, renderer = gifski_renderer("Top10_Confirmed_Cases.gif"))

```
<br>
<br> **Insights**
<br> 1. From the daily rise trend graph, we observe that **Maharashtra** has shown sharp rise in daily number of cases. So it can be classified as a **COVID-19 HOTSPOT**. **Delhi, Gujarat and Tamil Nadu** are next in line. So, steps must be taken to prevent these states to turn into a hotspot.
<br>
<br> 2. From the beds per Active Cases graph, we see that **Maharashtra** has very small ratio of beds to patients (17.36). And it has the highest number of cases in India. That means, if more beds are not made available soon, the **Maharashtra Govt.** may have to set up temporary hospitals like the one made by **Iran** and **China**.
<br>
<br> 3. As you can see in the animation, the first ever case of COVID-19 was found in Kerala. But, as time progresses, **Maharashtra** remains at the top for quite some time, whereas **Gujarat** rises to the second spot very quickly. 
<br>
<br> This concludes the project. Please refer to the other .html and .rmd files in the project that shows the **Novel CoronaVirus - India Dashboard**. 
<br>
<br> **THANK YOU!**